The increasing cost of happiness

### 2021-06-21 src/draft-SSM1.Rmd
Restored a consistent linear scale to Figure 1 x-axis

log_breaks <- c(log(12000), log(25000), log(50000), log(100000))

p1 <- figure1_data %>%
  rename(`Affective 1-100` = gh9) %>% 
  plot_log2(`Affective 1-100`, `Household income`) +
  scale_x_continuous(breaks = log_breaks, labels = c(12, 25, 50, 100)) +
  scale_fill_manual(values = "#C79999") +
  scale_color_manual(values = "#8F2727")

@@

p3 <- figure1_data %>%
  rename(`Cognitive 0-10` = losat) %>% 
  plot_log2(`Cognitive 0-10`, `Household income`) +
  scale_x_continuous(breaks = log_breaks, labels = c(12, 25, 50, 100)) +
  scale_fill_manual(values = "#b3cde0") +
  scale_color_manual(values = "#005b96")

>>>>

p1 <- figure1_data %>%
  rename(`Affective 1-100` = gh9) %>% 
  plot_log(`Affective 1-100`, `Household income`) +
  scale_fill_manual(values = "#C79999") +
  scale_color_manual(values = "#8F2727")

@@

p3 <- figure1_data %>%
  rename(`Cognitive 0-10` = losat) %>% 
  plot_log(`Cognitive 0-10`, `Household income`) +
  scale_fill_manual(values = "#b3cde0") +
  scale_color_manual(values = "#005b96")
